---
author: "Sihle"
title: "Assignments"
output: github_document
---
#Assignment 2

```{r quick_loo, echo=TRUE}
data("anscombe")
dim(anscombe)
names(anscombe)
head(anscombe)
tail(anscombe)
summary(anscombe)

```

#Assignment 3


```{r xy_plot, echo=FALSE, fig.height=8, fig.width=8, fig.align='center', fig.ext='svg', fig.path='./figures/'}

data("anscombe")
plot(anscombe$x1, anscombe$y1, xlab = 'x1', ylab = 'y1', pch = 22, col = 'green')
abline(lm(y1~x1, data=anscombe), lwd=2, col = 'grey')


```

#Assignment 4
##Chunk 1

```{r  data_import, echo=TRUE}

analgesicdf <- read.csv('analgesic.csv')
analgesicdf

```

##Chunk 2
```{r data_summary, echo=TRUE}
analgesicdf
dim(analgesicdf)
names(analgesicdf)
head(analgesicdf)
tail(analgesicdf)
summary(analgesicdf)

```

##Chunk 3
```{r data_tidy, echo=TRUE}
library(dplyr)
library(tidyr)

df1<-gather(analgesicdf, key = One, value = Two, Measurement_1, Measurement_2, Measurement_3)
df2<-group_by(df1, ID, Group)
df3<-summarise(df2, mean(Two))
print(df1)
print(df2)
print(df3)
```

#Assignment 5
##Chicken weights

* Null Hypothesis: The chicks' weights are not dependent on the feed.
* Alternative Hypothesisi: The chicks' weights are dependent on the feed.

```{r echo=TRUE}
chw <- read.csv('chick-weights (1).csv')
chw

#boxplot
plot(chw$feed, chw$weight)

#One-way anova
chw1 <- aov(chw$weight ~ chw$feed, data = chw)
summary(chw1)




```
* Test Assumptions- there are more than 2 groups and the data is parametric.

* df=5
* p value =5.94e-10
* we reject the null hypothesis. The chicks' weights are dependent on the type of feed. 

***

##The Hot Zone

* Null Hypothesis-The gastroenteritis is not caused by drinking contaminated water.
* Alternative Hypothesis- Gatroenteritis is caused by drinking contaminated water.

```{r echo=TRUE}
gast<- read.csv('gastroenteritis (2).CSV')
gast

#cross tabulating
gast1 <- table(gast$Consumption, gast$Outcome)
gast2 <- xtabs(~Consumption + Outcome, data =gast)

#barplot
gast3 <- barplot(gast2, beside = TRUE)

#chi squared test
gast4 <- chisq.test(gast2, correct = TRUE)
gast4





```
* Test Assumptions- There was random sampling, the observations are independent and the sample is large.

* x-squared=0.23
* df=2
* p-value=2.2e-16
* We reject the null hypothesis. There is a correlation between drinking contaminated water and falling ill. 

***

##Nausea

* Null Hypothesis-The chemotherapy does not cause nausea.
* Alternative Hypothesis- Chemotherapy causes nausea.

```{r echo=TRUE}
naus <- read.csv('nausea (1).csv')
naus

#line graph
plot(naus$Nausea_before~ naus$Patient, type = 'l',  col = 'blue', ylim = c(0,6))
lines(naus$Nausea_after~ naus$Patient, col = 'red')
legend("top", c('Nausea Before', 'Nausea after'), fill = c('blue', 'red'))

#wilcox
wilcox.test(naus$Nausea_before, naus$Nausea_after, data = naus)

```
*Test Assumptions- We are comparing 2 groups and the data is ordinal.

* W=52.5
* p-value=0.034
* We reject the null hypothesis. Chemotherapy does cause nausea. 



